Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
- label chuncks - conf & lift of SR grade

@@

```{r my_SR function}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_cspade <- function(data){

@@

```{r}
my_ruleInduction <- function(rules){

@@

```{r}
make_SR <- function(data, data_support, type_rule){

@@

### take -> take
```{r}
SR <- list()

SR$taken <- sequences$taken %>%
  make_SR(
    data_support = d_support$TNT, 
    type_rule = rate.take
  )
```

### fail -> fail
```{r}
SR$PF <- sequences$PF %>%

@@

### low grade -> low grade
```{r}
SR$HL <- sequences$HL %>%

@@

### not take -> fail
```{r, eval = FALSE}

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r, eval = FALSE}
SR$G <- sequences$G %>%

  make_SR %>%

  # rhs is grade less than 6
  filter(
    str_detect(rhs, "6")
    )
```

@@

### Save Sequences Rules
```{r}
#
# Save Sequence rules
save(
  SR,
  file = "App/SR.RDATA"
)

>>>>

    mutate(
      count = support * n_students
    ) %>%

@@

```{r my_cspade function}
my_cspade <- function(data){

@@

```{r my_ruleInduction}
my_ruleInduction <- function(rules){

@@

```{r make_SR}
make_SR <- function(data, data_support, type_rule){

@@

### take -> take
```{r SR taken}
SR <- list()

SR$taken <- sequences$taken %>%

  make_SR(
    data_support = d_support$TNT, 
    type_rule = rate.take
  )
```

### fail -> fail
```{r SR PF}
SR$PF <- sequences$PF %>%

@@

### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

@@

### not take -> fail
```{r SR TPF, eval = FALSE}

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%

  my_cspade %>%
  clean_rules %>%

  # Confidence & lift
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

  # Reduce number of rules
  filter(
    # exclude rules with same course on lhs and rhs
    lhs_course != rhs_course,
    # rhs is grade less than or equal to 6
    rhs_outcome == 6
    ) %>%

  # for each combination of course (lhs and rhs), keep AR with highest lift (most informative)
  group_by(
    lhs_course,
    rhs_course
    ) %>%
  top_n(
    n = 1,
    lift
    ) %>%
  ungroup
```

@@

### Save Sequences Rules
```{r SR save}
#
# Save Sequence rules
save(
  SR,
  file = "App/SR.RDATA"
)
